### 2023-02-17 paper/content.tex
Fix some typos (from overleaf)

Several branches of Earth Sciences have demonstrated the importance of the
``spatiality" of the data on a microscopic scale, mainly in geochemistry and
geochronology applications where it is possible to perform punctual analysis
and compositional maps, allowing significant advances in the understanding of
igneous, metamorphic and sedimentary processes \citep{Verberne2020, Barnes2019,
Davidson2007}. Classical paleomagnetic techniques, on the other hand, consist
in analyzing bulk samples, where the magnetic signal of a single specimen is
the result of the sum of moments of a large assembly of ferromagnetic grains
\citep{Dunlop1997}. Typically, a standard paleomagnetic sample of
approximately \qty{10}{\cm\cubed} would contain hundreds of thousands
to millions of magnetic particles with sizes varying from magnetically stable
single-domain (SD) and vortex state grains (also called pseudo-single domain,
PSD) with sizes below \qty{1}{\um}, to large ($\gg \qty{1}{\um}$) grains with
multi-domain (MD) magnetic structures, which are less stable magnetic recorders
\citep{Berndt2016}. These large MD grains usually conceal the signal of the SD
and PSD grains, and techniques of stepwise thermal and magnetic treatments are
needed to unveil the more stable and reliable magnetic record
\citep{Tauxe2018}. Recently, magnetic microscopy techniques opened the
possibility of performing magnetic maps at the micro-scale and recovering the
magnetization of each grain, therefore enabling the separate analysis of stable
and unstable magnetic particles \citep{DeGroot2018, Lima2014, Weiss2007,
DeGroot2014}.

In order to apply magnetic microscopy to paleomagnetic studies, it is necessary
to recover from the magnetic images a large amount of individual magnetic
moments, corresponding to at least tens of thousands of stable fine-grained
grains ($< \qty{1}{\um}$), in order to provide statistical significance to the
remanence vector \citep[e.g.][]{Berndt2016}. Nowadays, with the development of
magnetic microscopy techniques, this task is no longer limited by the
resolution of magnetic microscopes \citep{Fu2020, Weiss2007, DeGroot2018,
Glenn2017, Lima2014}, but essentially by the intrinsic problem presented by the
ambiguity in the inversion of potential field data \citep{Barbosa2011,
DeGroot2021, Oliveira2015Estimation}, and ultimately by the lack of a fast and
automated way to recover such a large number of individual magnetic moments
from a set of magnetic images \citep{CortesOrtuno2022, Lima2013, Lima2009}. A
solution to the non-uniqueness of magnetic moment inversion is to add
independent a priori information, such as the position of the ferromagnetic
particles \citep{Fabian2019}. This can be obtained, for example, from X-ray
computed tomography \citep[microCT; ][]{Fabian2019, DeGroot2021, DeGroot2018}.
Nonetheless, the standard microCT techniques do not provide adequate resolution
to resolve the finer and more stable magnetic grains \citep{CortesOrtuno2022,
DeGroot2021}, whereas other more sophisticated techniques such as ptychographic
X-ray tomography \citep[e.g., ][]{Maldanis2020} are not readily available and
too time-consuming to be routinely used in paleomagnetic studies.

@@

\begin{enumerate}
\item Calculate the \textit{total gradient amplitude} (TGA), also known as the
  3D analytic signal \citep{Roest1992Magnetic}, of the observed vertical
  component of the magnetic field. The TGA is entirely positive and tends to be
  more concentrated on top of the magnetic field sources than the observed
  magnetic field. The derivative calculation also acts as a high-pass filter,
  removing long-wavelength noise from the data.
\item Apply a contrast stretching method to rescale the TGA to a new range
  defined by the lower and upper percentiles of the data in order to highlight
  the weaker signals, either coming from small or from deep-seated particles.
\item Use the Laplacian of Gaussian (LoG) method \citep{Kong2013} on the
  rescaled TGA data to estimate the position and size of data windows
  containing the signal of each particle.
\end{enumerate}

@@

\noindent
and likewise for the $y$ and $z$ directions, in which $\Delta x$ is the grid
spacing (assumed to be equal in the $x$ and $y$ directions). For the $z$
component, $\Delta z = \Delta x$ and $f(x, y, z + \Delta z)$ and
$f(x, y, z - \Delta z)$ are calculated by upward and downward continuation,
respectively, performed in the wavenumber domain. The 2D maps of the $x$, $y$,
and $z$ derivates will also be used in the Euler Deconvolution step described
below, which is known to be highly sensitive to noise in the derivatives
\citep{Saleh2012Applying}. This is why e prefer the finite-differences based
derivatives, which are less prone to amplifying short-wavelength noise than
those calculated in the wavenumber domain through the Fast Fourier Transform
(FFT).

Once we have obtained a TGA image, we apply a contrast stretching method to
rescale the TGA values in order to highlight the weaker signals present in the
image. This is a necessary step to make sure that the blob detection algorithm
is able to identify particles causing both weak and strong signals. The
following contrast stretching operation is performed per pixel of the TGA image

@@

The rescaled TGA image is then used as input for a Laplacian of Gaussian (LoG)
blob detection algorithm \citep{Kong2013}. This method is able to identify the
location and size of multiple windows in the image containing ``blobs''. In our
case, the blobs are the rescaled TGA field of each particle and the LoG method
detects the local TGA maxima. The LoG method is particularly well suited for
the detection of bright blobs on a dark background at the expense of a longer
computation time \citep{Han2016}. For the image sizes routinely found in
magnetic microscopy, the computation is fast and only needs to be performed
once per image.

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=0.75\linewidth]{figures/simple-synthetic-dipole-moment.png}
\caption{
  CAPTION NEEDED
}
\label{fig_synthetic_simple_results}
\end{figure}

The central positions of each source obtained with ED were used as an input
parameter for inverting the vertical magnetic field. The inversion produced a
least squares (or robust) approximation solution for the vector of Cartesian
magnetic moments $m_x, m_y, m_z$ and the corresponding magnetization directions
(D and I) and intensity of magnetic moment $m$. We also obtained the
uncertainty propagation of this inversion, using Equation (REFERENCE NEEDED)
and considering $\sigma$ = 15 nT.\\

\begin{table}[t]
  \begin{center}
    \small
  \input{simple-synthetic-results.tex}
  \end{center}
  \caption{Meh}
\end{table}

\citet{Oliveira2015Estimation} proved that the magnetization directions (D and
I) recovered by the least squares estimator are sensitive to variations in the
horizontal coordinates of the center of the magnetic sources, but are
practically insensitive to variations in depth. Thus, they consider the Euler
deconvolution method as an adequate technique to estimate the central positions
that will be used as a priori information for inversion. This occurs mainly
because, when well performed, the recovery of the horizontal coordinates of the
source central position is considerably accurate, while the vertical coordinate
can undergo greater variation even though it still provides satisfactory
results \citep{Silva20033D, Melo2013}.

>>>>

Several branches of Earth Sciences have demonstrated the importance of the
``spatiality" of the data on a microscopic scale, mainly in geochemistry and
geochronology applications where it is possible to perform punctual analysis
and compositional maps, allowing significant advances in the understanding of
igneous, metamorphic and sedimentary processes \citep{Verberne2020, Barnes2019,
Davidson2007}. Classical paleomagnetic techniques, on the other hand, consist
in analyzing bulk samples, where the magnetic signal of a single specimen is
the result of the sum of moments of a large assembly of ferromagnetic grains
\citep{Dunlop1997}. Typically, a standard paleomagnetic sample of
approximately \qty{10}{\cm\cubed} would contain hundreds of thousands
to millions of magnetic particles with sizes varying from magnetically stable
single-domain (SD) and vortex state grains (also called pseudo-single domain,
PSD) with sizes below \qty{1}{\um}, to large ($\gg \qty{1}{\um}$) grains with
multi-domain (MD) magnetic structures, which are less stable magnetic recorders
\citep{Berndt2016}. These large MD grains usually conceal the signal of the SD
and PSD grains, and techniques of step-wise thermal and magnetic treatments are
needed to unveil the more stable and reliable magnetic record
\citep{Tauxe2018}. Recently, magnetic microscopy techniques opened the
possibility of performing magnetic maps at the micro-scale and recovering the
magnetization of each grain, therefore enabling the separate analysis of stable
and unstable magnetic particles \citep{DeGroot2018, Lima2014, Weiss2007,
DeGroot2014}.

In order to apply magnetic microscopy to paleomagnetic studies, it is necessary
to recover from the magnetic images a large amount of individual magnetic
moments, corresponding to at least tens of thousands of stable fine-grained
grains ($< \qty{1}{\um}$), in order to provide statistical significance to the
remanence vector \citep[e.g., ][]{Berndt2016}. Nowadays, with the development of
magnetic microscopy techniques, this task is no longer limited by the
resolution of magnetic microscopes \citep{Fu2020, Weiss2007, DeGroot2018,
Glenn2017, Lima2014}, but essentially by the intrinsic problem presented by the
ambiguity in the inversion of potential field data \citep{Barbosa2011,
DeGroot2021, Oliveira2015Estimation}, and ultimately by the lack of a fast and
automated way to recover such a large number of individual magnetic moments
from a set of magnetic images \citep{CortesOrtuno2022, Lima2013, Lima2009}. A
solution to the non-uniqueness of magnetic moment inversion is to add
independent prior information, such as the position of the ferromagnetic
particles \citep{Fabian2019}. This can be obtained, for example, from X-ray
computed tomography \citep[microCT; ][]{Fabian2019, DeGroot2021, DeGroot2018}.
Nonetheless, the standard microCT techniques do not provide adequate resolution
to resolve the finer and more stable magnetic grains \citep{CortesOrtuno2022,
DeGroot2021}, whereas other more sophisticated techniques such as ptychographic
X-ray tomography \citep[e.g., ][]{Maldanis2020} are not readily available and
too time-consuming to be routinely used in paleomagnetic studies.

@@

\begin{enumerate}
\item Calculate the \textit{total gradient amplitude} (TGA), also known as the
  3D analytic signal \citep{Roest1992Magnetic}, of the observed vertical
  component of the magnetic field. The TGA is entirely positive and tends to be
  more concentrated on top of the magnetic field sources than the observed
  magnetic field. The derivative calculation also acts as a high-pass filter,
  removing long-wavelength noise from the data.
\item Apply a contrast stretching method to re-scale the TGA to a new range
  defined by the lower and upper percentiles of the data in order to highlight
  the weaker signals, either coming from small or from deep-seated particles.
\item Use the Laplacian of Gaussian (LoG) method \citep{Kong2013} on the
  re-scaled TGA data to estimate the position and size of data windows
  containing the signal of each particle.
\end{enumerate}

@@

\noindent
and likewise for the $y$ and $z$ directions, in which $\Delta x$ is the grid
spacing (assumed to be equal in the $x$ and $y$ directions). For the $z$
component, $\Delta z = \Delta x$ and $f(x, y, z + \Delta z)$ and
$f(x, y, z - \Delta z)$ are calculated by upward and downward continuation,
respectively, performed in the wavenumber domain. The 2D maps of the $x$, $y$,
and $z$ derivatives will also be used in the Euler Deconvolution step described
below, which is known to be highly sensitive to noise in the derivatives
\citep{Saleh2012Applying}. This is why e prefer the finite-differences based
derivatives, which are less prone to amplifying short-wavelength noise than
those calculated in the wavenumber domain through the Fast Fourier Transform
(FFT).

Once we have obtained a TGA image, we apply a contrast stretching method to
re-scale the TGA values in order to highlight the weaker signals present in the
image. This is a necessary step to make sure that the blob detection algorithm
is able to identify particles causing both weak and strong signals. The
following contrast stretching operation is performed per pixel of the TGA image

@@

The re-scaled TGA image is then used as input for a Laplacian of Gaussian (LoG)
blob detection algorithm \citep{Kong2013}. This method is able to identify the
location and size of multiple windows in the image containing ``blobs''. In our
case, the blobs are the re-scaled TGA field of each particle and the LoG method
detects the local TGA maxima. The LoG method is particularly well suited for
the detection of bright blobs on a dark background at the expense of a longer
computation time \citep{Han2016}. For the image sizes routinely found in
magnetic microscopy, the computation is fast and only needs to be performed
once per image.

@@

\begin{figure}[!t]
\centering
\includegraphics[width=0.75\linewidth]{figures/simple-synthetic-dipole-moment.png}
\caption{
  CAPTION NEEDED
}
\label{fig_synthetic_simple_results}
\end{figure}

The central positions of each source obtained with ED were used as an input
parameter for inverting the vertical magnetic field. The inversion produced a
least squares (or robust) approximation solution for the vector of Cartesian
magnetic moments $m_x, m_y, m_z$ and the corresponding magnetization directions
(D and I) and intensity of magnetic moment $m$. We also obtained the
uncertainty propagation of this inversion, using Equation (REFERENCE NEEDED)
and considering $\sigma = \qty{15}{\nano\tesla}$.

\begin{table}[t]
  \begin{center}
    \small
    \input{simple-synthetic-results.tex}
  \end{center}
  \caption{Meh}
  \label{tab_synthetic_simple_results}
\end{table}

\citet{Oliveira2015Estimation} proved that the magnetization directions (D and
I) recovered by the least squares estimator are sensitive to variations in the
horizontal coordinates of the center of the magnetic sources, but are
practically insensitive to variations in depth. Thus, they consider the Euler
deconvolution method as an adequate technique to estimate the central positions
that will be used as prior information for inversion. This occurs mainly
because, when well performed, the recovery of the horizontal coordinates of the
source central position is considerably accurate, while the vertical coordinate
can undergo greater variation even though it still provides satisfactory
results \citep{Silva20033D, Melo2013}.
